---
description: "Generic Script for Logistic Regression Testing"
output: html_document
params:
  data: NULL
  outcomes: NULL
  predictors: NULL
  covariates: NULL
  confounders: NULL
  plot_subtitle: ""
  page_title: ""
  output_objects_filename: "tmp.covlogreg.RData"
  output_objects_filepath: "~/Projects/asthma/asthma-research/data/objects/"
---

```{r, include=FALSE}
page_title <- params$page_title
```

# `r page_title`

### Import utilities

```{r import}
source("~/Projects/asthma/asthma-research/code/r/PROJECT_GLOBAL_CONFIGS.R")
import.project_utils()
```

### Import libraries
```{r, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

install_package_if_missing(package_names = c("DT", "knitr", "ggplot2"))
library(DT)
library(knitr)
library(ggplot2)
```

## Fit logistic regression models to all variables in the data
```{r create_models, warning=FALSE}
data <- params$data
outcomes <- params$outcomes
predictors <- params$predictors
covariates <- params$covariates
confounders <- params$confounders

glm_output <- .run_multiple_logreg_tests(
  outcomes = outcomes, 
  predictors = predictors,
  covariates = covariates,
  confounders = confounders, 
  data = data,
  test = "binomial"
)

summary_pval_tables <- create_pval_odds_summary_table_with_covariates(glm_output)
```

## Variables investigated
```{r}
DT::datatable(data.frame(outcomes = outcomes))
DT::datatable(data.frame(predictors = predictors))
DT::datatable(data.frame(covariates = covariates))
DT::datatable(data.frame(confounders = confounders))
```

## Results

Show results for each outcome tested. 

```{r create-markdown-chunks-dynamically, include=FALSE}
out = c()
tables <- list()
section_headers <- list()

i <- 1
for (outcome in outcomes) {
  section_headers[[i]] <- paste0("Test results for association with outcome: ", outcome)
  table_for_outcome <- summary_pval_tables$summary_table[[outcome]]
  table_for_outcome <- table_for_outcome[order(table_for_outcome$fdr.adj.p), ]
  tables[[i]] <- table_for_outcome
  i <- i + 1
}
for (i in 1:length(tables)) {
  knit_expanded <- paste0("\n\n\n### `r section_headers[[", i, "]]` \n\n```{r results='asis', echo=FALSE, fig.height = 12, fig.width = 14}\n\nDT::datatable(tables[[", i, "]], options = list(scrollX = TRUE))\n\n\n\ncreate_pval_comparison_plot(summary_pval_tables, handle_pred_category = TRUE, plot_subtitle = params$plot_subtitle)\n\n\n```")
  out = c(out, knit_expanded)
}
```

`r paste(knit(text = out), collapse = '\n')`

### Output data
Use these files and objects for downstream analysis.
```{r write_to_files}
if (!is_string_blank(params$output_objects_filename)) {
  save(glm_output, 
       summary_pval_tables, 
       list = c("glm_output", "summary_pval_tables"), 
       file = generate_output_objects_filepath(params$output_objects_filename))
} else if (is_string_blank(params$output_objects_filename) && !is_string_blank(params$output_objects_filepath)) {
  save(glm_output, 
       summary_pval_tables, 
       list = c("glm_output", "summary_pval_tables"), 
       file = params$output_objects_filepath)
}
```
